### 2014-12-01 docs/ms.Rmd
Updated the ms with the more recent analysis code to call on various proportions.

Our search returned a total of 216 papers, however, only `r nrow(coldat)` met our criteria and were included in the final analysis. Overall, `r specs+both` studies used a spectrometer to measure colour, while `r cam+both` used a camera. Of these studies, `r both` quantified colour using both a spectrometer and a camera. Reporting of the make and model of the spectrometer and camera was high (Figure 1, spectrometers = `r round(specModel, digits = 2)`% and cameras = `r round(camModel, digits = 2)`%), however, only `r round(CamLight, digits = 2)`%  and `r round(specLight, digits = 2)`% of camera and spectrometer studies reported a light source. In addition, the number of reflectance spectra and pixels averaged were only reported in `r round(specAVG, digits = 2)`% and `r round(camAVG, digits = 2)`% of studies, respectively. Surprisingly, dark standards were only reported in `r round(drk_std, digits = 2)`% of the spectrometer studies, while white standards were reported in `r round(white_stdspec, digits = 2)`%. Studies quantifying spectral reflectance often did not report the integration time of the spectrophotmeter (`r round(intTime, digits = 2)`%), or the angle of the optical probe relative to the surface (`r round(angle, digits = 2)`%) or distance (`r round(dist, digits = 2)`%) the probe was held from the measurement surface.

@@

Most studies using visual models analysed their data using receptor-noise models (`r vismod_type[3]` of `r sum(vismod_type)` studies), while others used the colour hexagon (`r vismod_type[1]` studies), or tetrahedral colour space (`r vismod_type[4]` studies) approach. Case specific models were used in `r vismod_type[2]` papers. Of visual modelling papers, `r round(prop_irrad, digits =2)`% reported the type of irradiance when necessary, `r round(prop_spvismod, digits = 2)`% the species modelled as a receiver, and `r round(propvis_mod_param, digits = 2)`% made explicit and complete mention of the parameters they used (e.g. cone densities, signal-to-noise ratios). The background used in visual models was reported `r round(prop_bkg, digits = 2)`% of the time. The type of receptor noise modelled was reported in only `r round(prop_noise, digits = 2)`% of the studies. Explicit mention of the type of quantum catch (`r round(prop_qcatch, digits = 2)`% of studies), or whether photoreceptor adaptation (`r round(prop_adap, digits = 2)`%) was modelled, was not common.

@@

While all criteria are important, some deserve special attention. In particular, we found that the types of light sources, numbers of pixels or spectra averaged, and types of standards used (i.e. white and black reference samples) are under-reported, each of which is critical to repeatability and cross-comparison. Similarly, the distance and angle of the optical probe relative to the measurment surface and collector should be standard reporting for all studies using spectrophometry, as variation in these factors can lead to dramatically different results in some cases (REFS). Visual models were regularly used to analyse spectral data, however, there were many important aspects of the analysis that were seldom reported. These included the type of quantum catch used, whether photoreceptor adaptation was modelled and the type of noise used in receptor-noise models. This is problematic because... Also, photoreceptor densities should be reported where possible even if using standard avian photorecptor densities because.... These all have important consequences on downstream analysis and the reproducibility of colour signal quantification [e.g. @kemp_ornamental_2008; @santos_comparison_2007]. We also recommend the presentation of spectral reflectance curves where possible. These figures allow for the rapid assesment of the nature and quality of the data, independent of downstream processing (if the conditions under which they were captured is comprehensively reported. We found that only `r round(fig, digits = 2)`% of studies using spectral reflectance data had a figure showing these curves. When possible, we also recommend that authors justify data capture and analytical approaches - something few studies we investigated explicitly outlined.

>>>>

Our search returned a total of 216 papers, however, only `r nrow(coldat)` met our criteria and were included in the final analysis. Overall, `r specs+both` studies used a spectrometer to measure colour, while `r cam+both` used a camera. Of these studies, `r both` quantified colour using both a spectrometer and a camera. Reporting of the make and model of the spectrometer and camera was high (Figure 1, spectrometers = `r round(specModel, digits = 2)`% and cameras = `r round(camModel, digits = 2)`%), however, only `r round(propCam_fin["prop_light_source"], digits = 2)`%  and `r round(propSpec_fin["prop_light_source"], digits = 2)`% of camera and spectrometer studies reported a light source. In addition, the number of reflectance spectra and pixels averaged were only reported in `r round(propSpec_fin["prop_specpix_avg"], digits = 2)`% and `r round(propCam_fin["prop_specpix_avg"], digits = 2)`% of studies, respectively. Surprisingly, dark standards were only reported in `r round(propSpec_fin["prop_dark_std"], digits = 2)`% of the spectrometer studies, while white standards were reported in `r round(propSpec_fin["prop_white_stdspec"], digits = 2)`%. Studies quantifying spectral reflectance often did not report the integration time of the spectrophotmeter (`r round(propSpec_fin["prop_int_time"], digits = 2)`%), or the angle of the optical probe relative to the surface (`r round(propSpec_fin["prop_spec_angle"], digits = 2)`%) or distance (`r round(propSpec_fin["prop_spec_dist"], digits = 2)`%) the probe was held from the measurement surface.

@@

Most studies using visual models analysed their data using receptor-noise models (`r vismod_type[3]` of `r sum(vismod_type)` studies), while others used the colour hexagon (`r vismod_type[1]` studies), or tetrahedral colour space (`r vismod_type[4]` studies) approach. Case specific models were used in `r vismod_type[2]` papers. Of visual modelling papers, `r round(propSpec_fin["prop_irrad_type"], digits =2)`% reported the type of irradiance when necessary, `r round(propSpec_fin["prop_vis_mod_sp"], digits = 2)`% the species modelled as a receiver. The background used in visual models was reported `r round(propSpec_fin["prop_vis_mod_bkg"], digits = 2)`% of the time. The type of receptor noise modelled was reported in only `r round(propSpec_fin["prop_vis_mod_noise_type"], digits = 2)`% of the studies. Explicit mention of the type of quantum catch (`r round(propSpec_fin["prop_vis_mod_qcatch"], digits = 2)`% of studies), or whether photoreceptor adaptation (`r round(propSpec_fin["prop_vis_mod_adapt"], digits = 2)`%) was modelled, was not common.

@@

While all criteria are important, some deserve special attention. In particular, we found that the types of light sources, numbers of pixels or spectra averaged, and types of standards used (i.e. white and black reference samples) are under-reported, each of which is critical to repeatability and cross-comparison. Similarly, the distance and angle of the optical probe relative to the measurment surface and collector should be standard reporting for all studies using spectrophometry, as variation in these factors can lead to dramatically different results in some cases (REFS). Visual models were regularly used to analyse spectral data, however, there were many important aspects of the analysis that were seldom reported. These included the type of quantum catch used, whether photoreceptor adaptation was modelled and the type of noise used in receptor-noise models. This is problematic because... Also, photoreceptor densities should be reported where possible even if using standard avian photorecptor densities because.... These all have important consequences on downstream analysis and the reproducibility of colour signal quantification [e.g. @kemp_ornamental_2008; @santos_comparison_2007]. We also recommend the presentation of spectral reflectance curves where possible. These figures allow for the rapid assesment of the nature and quality of the data, independent of downstream processing (if the conditions under which they were captured is comprehensively reported. We found that only `r round(propSpec["refl_fig"], digits = 2)`% of studies using spectral reflectance data had a figure showing these curves. When possible, we also recommend that authors justify data capture and analytical approaches - something few studies we investigated explicitly outlined.
